---
title: "Data Products Final Project Presentation"
author: "Joseph Imperato"
date: "4/30/2020"
output: ioslides_presentation
---

```{r setup,warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Interactive Graphing and Data Analysis

#### The Application Delivers the Capability to **Dynamically Input Values**
- The Number of Individuals for Each Group can be Continually Updated
- The Graphs will then be **Automatically Updated** Every Time a new Count is Inputted
- The Application Enables the Ability to Change the Age Range of the Population
- A Random Set People will be added to Each Group based on Count and Age Range Selected
- Each Group will be Divided up into Quartiles and the Graphs will be **Dynamically Updated**

## Ability to Continually Update Group Counts

#### The Application Provides Ability to Update Population Counts for 2 Graphs
- Provides **2 Different Sections** to Update Populations
- Each Population Section will Automatically Update the Associated Graph
- *Below is a Sample of the Population Input Sections*

```{r,warning= FALSE, echo = FALSE}
temp <- readline(prompt = "Input Number of People for Group 1 - minimum 50 and maximum 1000: ")
temp2 <- readline(prompt = "Input Number of People for Group 2 - minimum 50 and maximum 1000: ")

```
#### *There is also the Ability to Change the Age Range of the Groups*

## Dynamic Graphs
#### Ages of Individuals Randomly Generated
#### Graphs Based on the Quartile of the Age Range

```{r,warning= FALSE, echo = FALSE}

number_of_points1 = 400
number_of_points2 = 600

    min1 <- 45
    max1 <- 95
    range <- max1-min1
    
    q1 <- min1+range*1/4
    q2 <- min1 + range *1/2
    q3 <- min1 + range *3/4
    data1 <- runif(number_of_points1, min1, max1)
    d1age <-as.data.frame(data1)
    d1age$group <- ifelse(d1age$data1 >= min1 & d1age$data1 < q1, "1st Q", ifelse(d1age$data1 >= q1 & d1age$data1 < q2, "2nd Q", ifelse(d1age$data1 >= q1 & d1age$data1 < q3, "3rd Q","4th Q")))
    tab_d1age<-(table(d1age$group))
    
data2 <- runif(number_of_points2, min1, max1)
    d2age <-as.data.frame(data2)
    d2age$group <- ifelse(d2age$data2 >= min1 & d2age$data2 < q1, "1st Q", ifelse(d2age$data2 >= q1 & d2age$data2 < q2, "2nd Q", ifelse(d2age$data2 >= q2 & d2age$data2 < q3, "3rd Q", "4th  Q")))
    tab_d2age<-(table(d2age$group))

main1 = paste('Minumum Age is', min1, 'Maximum Age is', max1)
    ylab1 = paste('Frequency of Quartile for Patient Count', number_of_points1)
    ylab2 = paste('Frequency of Quartile for Patient Count', number_of_points2)

   
     par(mfrow = c(1,2))
     
  plot(tab_d1age,xlab = "Age Range Quartiles", ylab = ylab1,main = main1 , col = "green", type = "h", lwd = "8",cex.lab =.7,cex.axis = .7,cex.main=.9,cex=.7)
    
  plot(tab_d2age,xlab = "Age Range Quartiles", ylab = ylab2, main = main1, col = "blue", type = "h", lwd = "8",cex.lab=.7,cex.axis = .7,cex.main=.9,cex=.7)
``` 

## Statistical Analysis
#### Chi Square Test Run to Determine Independence of 2 Groups

```{r,warning= FALSE, echo = TRUE}

chisq.test(tab_d1age,tab_d2age)
```

#### As Expected P value > .05 (Fail to Reject Null Hypothesis)
#### Demonstrating that the Data Sets are Independent
